### 2021-12-09 input/proposal.tex
mostly todo and notes to discuss to improve

\begin{definition}[\label{def:fs}\underline{F}orwarding of
    \underline{s}taleness (FS)]
  %
  A \process $x$ delivers and forwards a received staleness
  notification if it targets its best up-to-date delivered message:\\
  \TODO{$(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.}\\
  $\textup{last}~D = \alpha_s \wedge d_x(\alpha_s) \rightarrow r_x(\delta_s)
  \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
\end{definition}

@@

As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
wrongfully believes that it belongs to $a$'s partition when $a$
already deleted it, but it could contribute to its inconsistency by
blocking farther but up-to-date messages from actual sources. To reach
consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to detect possibly blocking conditions 
\item to purge all stale messages from the system
\item enabling up-to-date notifications to eventually echo back to
  every \process.
\end{inparaenum}

@@

\begin{definition}[\label{def:fsplus}$\textup{FS}^+$: forwarding
  staleness downstream]
  To \NAMEB staleness downstream, a node $x$ delivers and forwards a
  received staleness notification if it is not yet delivered and it
  comes from the path of delivery of its best up-to-date delivered
  message. \TODO{more.}
\end{definition}

>>>>

\begin{definition}[\label{def:fs}\underline{F}orwarding of
  \underline{s}taleness (FS)]
  % 
  \TODO{A source broadcasts.}
  A \process $x$ delivers and forwards \TODO{at most once} a received staleness
  notification if it targets its best up-to-date delivered message:\\
  \TODO{$(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.}\\
  $\textup{last}~D = \alpha_s \wedge d_x(\alpha_s) \rightarrow r_x(\delta_s)
  \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
\end{definition}

@@

As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
wrongfully believes that it belongs to $a$'s partition when $a$
already deleted it, but it could contribute to its inconsistency by
blocking farther but up-to-date messages from actual sources. To reach
consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to detect possibly blocking conditions 
\item to purge all stale messages from the system
\item enabling up-to-date notifications to eventually echo back to
  every \process.
\end{inparaenum}
\TODO{A lot of blockings occur, only that of example is a problem.
  Could be $b$ or $c$ that detects? We put burden on $c$ since
  unconsistency starts here. Problem: how to make sure that $c$
  receives a staleness notification in this case?}

@@

\begin{definition}[\label{def:fsplus}$\textup{FS}^+$: forwarding
  staleness downstream]
  \TODO{Any process broadcast.}  A node $x$ delivers and forwards a
  received staleness notification if it is not yet delivered and it
  comes from the path of delivery of its best up-to-date delivered
  message. \TODO{more.}
\end{definition}
